\documentclass{grattan}


% Comments are deployed by the % sign; everything after % is ignored by the compiler.
% Please do not put comments before \documentclass as these are reserved for TeX directives.
% add_to_dictionary: SSBs i ii iii CESE AYP RCTs frontline pay-offs ATAR judgments


\addbibresource{bib/GonskiSub.bib}

%Note from CC: All refs should go in GonskiSub.bib for now. 

\author{Julie Sonnemann and Peter Goss}
\title{The Commonwealth’s role in improving schools}

\GrattanReportNumber{2018-02}

\ReportOrWorkingPaper{Report}

\acknowledgements{%
This Report was written by Julie Sonnemann and Peter Goss.

We would like to thank the members of Grattan Institute's School Education Program Reference Group for their helpful comments, as well as numerous government and industry participants and officials for their input.

The opinions in this report are those of the authors and do not necessarily represent the views of Grattan Institute's founding members, affiliates, individual board members reference group members or reviewers.
Any remaining errors or omissions are the responsibility of the authors.

Grattan Institute is an independent think-tank focused on Australian public policy.
Our work is independent, practical and rigorous.
We aim to improve policy outcomes by engaging with both decision-makers and the community.

For further information on the Institute's programs, or to join our mailing list, please go to: \textcolor{blue}{\url{http://www.grattan.edu.au/}}.

{\footnotesize
This report may be cited as: 
Sonnemann, J. and Goss, P\@. (2018). \emph{\mytitle}. Grattan Institute.

ISBN: 978-0-6482307-2-4

All material published or otherwise created by Grattan Institute is licensed under a Creative Commons Attribution-NonCommercial-ShareAlike 3.0 Unported License\par
}
}


\begin{document}

\input{travis/Text/Overview}
\contentspage
\listoffigures
\input{travis/Text/Recommendations}
\input{travis/Text/Chapter1}
\input{travis/Text/Chapter2}
\input{travis/Text/Chapter3}
\input{travis/Text/Chapter4}
\input{travis/Text/Chapter5}
\input{travis/Text/Chapter6}
\input{travis/Text/Appendix}

\printbibliography

\end{document}







